Summer 2025 ToDo

### 2025-06-13 Relations/Paper/Definitions.tex
Various small changes

The file \texttt{ClosureOperators.agda} verifies a number of properties of these operators
on relations needed in the subsequent development, including interaction between them,
monotonicity, preservation of logical equivalence, etc.
\apcomment{Edit/Improve this!}

@@

% \subsection{Confluence (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d. c \mstep d \bmstep b\]
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d. c \mstep d \bmstep b\]
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
        \[c \bmstep a \mstep b \implies c \rrstep d \brstep b\]
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if for all $b \in \NF_R$,
        \[c \bmstep a \mstep b \implies c \mstep b\]
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if for all $b, c \in \NF_R$,
        \[c \bmstep a \mstep b  \implies b \equiv c\]
    \end{description}
\end{definition}
% \begin{definition} Let $a \in A$.
%     \begin{description}
%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
%     \end{description}
% \end{definition}

@@

\begin{remark}
    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Subsection~\ref{subsec:counterexamples}.
    \apcomment{Provide a ref to a figure, eventually.}
\end{remark}

@@

\terese also defines the following property, which is not included in our formalization.

@@

Having a size function that maps all of $A$ to the natural numbers can be computationally taxing to satisfy.
Furthermore, it takes us outside of a purely relational theory. The weaker property $\gRP$ defined above will substitute $\gInc$ all places that require it. (For further discussion, see Subsection \ref{subsec:def}.)

@@

\apcomment{Make sure to move this stuff to Seq.agda!}

>>>>

The file \texttt{ClosureOperators.agda} verifies key properties of closure operators
on relations, including their monotonicity, preservation of equivalence, and interactions such as inclusions and equivalences between different closures.

@@

% \subsection{Confluence (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
        \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if for all $b \in \NF_R$,
        \[c \bmstep a \mstep b \implies c \mstep b\]
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if for all $b, c \in \NF_R$,
        \[c \bmstep a \mstep b  \implies b \equiv c\]
    \end{description}
\end{definition}
% \begin{definition} Let $a \in A$.
%     \begin{description}
%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
%     \end{description}
% \end{definition}

@@

\begin{remark}
    The implication $\UNto \implies \UN$ does not hold, as can be seen in Counterexample~\ref{CE:5} in Figure~\ref{fig:counterexamples}.
\end{remark}

@@

\terese $\,$ also defines the following property, which is not included in our formalization.

@@

Having a size function that maps all of $A$ to the natural numbers can be computationally taxing to satisfy.
Furthermore, it takes us outside of a purely relational theory. The weaker property $\gRP$ defined above will substitute $\gInc$ all places that require it. (For further discussion, see Subsection~\ref{subsec:def}.)

@@

\apcomment{Make sure to move this stuff to Seq.agda!}
\sacomment{This will create a circular dependency as Seq is used in properties (the increasing definition is needed for BP, CP, RP, SMseq, SRv2). Simple solution is to leave RP-iffRP in implications.agda.}
